\plaintitle

### 2016-09-21 Paper/proceedings.tex
Addressed Jeff Edits

We limited the Mechanical Turk participant pool to subjects from within the United States, with a prior task approval rating of at least 90\%. For validation, certain trials contained the actual (OLS) trend line, which subjects then needed to simply match. \jeff{But what if subjects honestly disagreed? Did we do this in the presence of outliers, for example?} We excluded the results of participants with poor performance on these validation questions. \jeff{What level of error constitutes poor performance?} Across the three reported experiments and pilots, we performed 7 such exclusions. We recruited additional participants to replace these excluded subjects. Based on timings from internal piloting, we paid each participant \$2 for their participation, for a target rate of \$8/hour.

@@

For each point set, we created a set of residual values, sampled evenly from a discretized Gaussian. \jeff{In what way was it discretized?} The bandwidth of this Gaussian controls both goodness of fit and dispersion of points (see Fig. \ref{fig:sigmas}). We permuted this set of residuals, and then applied them to points along a target trend. As heteroskedasticity introduced through permutation could alter the actual trend away from the target trend, we performed rejection sampling to ensure that the trend of the resulting points were within $10^{-7}$ of the target trend. We reused these residuals across all different trend types (linear, quadratic, or trigonometric). Fig. \ref{fig:trendtypes} shows these different trend types on the same set of residuals.

@@

We performed a three-way analysis of covariance (ANCOVA) of the effect of residual bandwidth, graph type and trend type on absolute error in estimation of trend lines. We included participant ids and the actual slope of the trend line as covariates. \jeff{Add a sentence here explicitly defining our error measure.}

@@

In general, the accuracy of slope estimation was high, with an interquartile mean of $0.06$ for slope values ranging from $\{-1,1\}$, corresponding to an accuracy of $17\%$ of the actual slope. \jeff{We use the term ``accuracy'' for two different measurements here, which is confusing. Also, a widow line.}

@@

Similar to the previous experiments, participants saw one of each of the three graph types, slope, and Gaussian residual bandwidth. \jeff{Awkward grammar for previous sentence.} The four outlier quantities $\{0,5,10,15\}$ was an additional factor. To maintain a manageable number of stimuli (piloting showed evidence of fatigue for more than 100 stimuli per trial), both the sign of the trend line (positive or negative), and the location of the outliers (beginning, first third, or end) were random factors, with each level apportioned to half and one third of the stimuli respectively. This resulted in 96 total stimuli, with an additional 4 validation stimuli otherwise excluded from analysis, in line with prior experiments.

>>>>

We limited the Mechanical Turk participant pool to subjects from within the United States, with a prior task approval rating of at least 90\%. For validation, additional trials, without ambiguities such as outliers or design differences, contained the actual (OLS) trend line, which subjects then needed to simply match.  We excluded the results of participants with average error greater than 0.2 (20 times the step size of the slider) on these validation questions. Across the three reported experiments and pilots, we performed 7 such exclusions. We recruited additional participants to replace these excluded subjects. Based on timings from internal piloting, we paid each participant \$2 for their participation, for a target rate of \$8/hour.

@@

For each point set, we created a set of residual values, sampled evenly from a Gaussian. The bandwidth of this Gaussian controls both goodness of fit and dispersion of points (see Fig. \ref{fig:sigmas}). We permuted this set of residuals, and then applied them to points along a target trend. As heteroskedasticity introduced through permutation could alter the actual trend away from the target trend, we performed rejection sampling to ensure that the trend of the resulting points were within $10^{-7}$ of the target trend. We reused these residuals across all different trend types (linear, quadratic, or trigonometric). Fig. \ref{fig:trendtypes} shows these different trend types on the same set of residuals.

@@

We performed a three-way analysis of covariance (ANCOVA) of the effect of residual bandwidth, graph type and trend type on error in estimation of trend lines. We included participant ids and the actual slope of the trend line as covariates. We defined error as the absolute difference between the slope of the OLS trend line, and the slope of the participant estimate.

@@

In general, the absolute error of slope estimation was low, with an interquartile mean of $0.06$ for slope values ranging from $\{-1,1\}$, corresponding to an error rate of $17\%$ of the actual slope.

@@

Similar to the previous experiments, participants saw one of each combination of factors: the three graph types, eight slopes, and four Gaussian residual bandwidths. The four outlier quantities $\{0,5,10,15\}$ was an additional factor. To maintain a manageable number of stimuli (piloting showed evidence of fatigue for more than 100 stimuli per trial), both the sign of the trend line (positive or negative), and the location of the outliers (beginning, first third, or end) were random factors, with each level apportioned to half and one third of the stimuli respectively. This resulted in 96 total stimuli, with an additional 4 validation stimuli otherwise excluded from analysis, in line with prior experiments.
